%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
  {Software Engineer} % Job title
    {Facebook} % Organization
    {Menlo Park, CA} % Location
    {Aug 2018 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Working on AdIndexer Infra team on Facebook ads.} 
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
  {Software Engineering Intern (Infrastructure)} % Job title
    {Facebook} % Organization
    {Seattle, WA} % Location
    {Sept 2017 - Dec 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed and deployed an indexer service which watches for changes and provides data regarding size of each Zookeeper node in Zookeeper ensemble using C++.}
      \item {Implemented clustering algorithm to group Zookeeper nodes with similar names to provide a useful breakdown of total Zookeeper size usage.}
      \item {Provided automatic detection of size growth of total Zookeeper ensemble which creates a report and notifies teams responsible for the growth.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
  {Software Engineering Intern (Backend)} % Job title
    {Coursera} % Organization
    {Mountain View, CA} % Location
    {Jan 2017 - April 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed scalable services for Coursera's Enterprise team using Scala, Cassandra, MySQL, and Kafka.}
      \item {Built notification system to remind users to enroll in courses, resulting in an increase in user engagement metrics.}
      \item {Developed peer recommendation system which allows users to recommend courses to other learners.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
  {Software Engineering Intern (Full-stack)} % Job title
    {PagerDuty} % Organization
    {San Francisco, CA} % Location
    {May 2016 - Aug 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed features for PagerDuty's Incident team using Scala, Cassandra, MySQL, Ruby on Rails, and Android.}
      \item {Maintained highly available Scala services responsible for aggregating and reliably delivering notifications to users.}
      \item {Built new incident management feature on PagerDuty's web and mobile platform.}
      \item {Implemented metrics system to improve visibility of critical system, allowing engineers to quickly identify issues. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {Software Engineering Intern (Front-end)} % Job title
    {Inkling} % Organization
    {San Francisco, CA} % Location
    {Aug 2015 - Dec 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed core Python API service, consumed across all Inkling products.}
      \item {Built Inkling's Backbone digital content reader app with Django middleware.}
      \item {Implemented key features in Inkling cross-title library search functionality.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {Software Engineering Intern (Full-stack)} % Organization
    {Boltmade} % Job title
    {Waterloo, ON} % Location
    {Jan 2015 - April 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Built multiple entire web applications with Ruby on Rails and AngularJS that were shipped to production.}
      \item {Developed both large scale applications and small-scale web applications from ground-up.}
      \item {Led weekly sprint planning meetings with clients and discussed design implementations.}
  \end{cvitems} 
    }
%---------------------------------------------------------
  % \cventry
  %   {Summer Student, IT Operations} % Organization
  %   {Legal Aid Ontario} % Job title
  %   {Toronto, ON} % Location
  %   {Summer 2014} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %     \item {Wrote bash scripts to parse large database and to automate processing of data.}
  % \end{cvitems} 
  %   }

\end{cventries}
