%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  % \cventry
  %   {Testing} % Organization/group
  %   {S.Korea} % Location
  %   {Jun. 2012 - PRESENT} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of experience/contributions/knowledge
  %       \item {Gained expertise in hardware hacking areas from penetration testing on several devices including wireless router, smartphone, CCTV and set-top box.}
  %       \item {Trained wannabe hacker about hacking technique from basic to advanced and ethics for white hackers by hosting annual Hacking Camp.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
  \cventry
    {\href{http://github.com/ernestwong/sudokusolver}{http://github.com/ernestwong/sudokusolver}} % Organization/group
    {Sudoku Puzzle OCR Cam Solver | Sudoku Solver} % Affiliation/role
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Android application which takes picture of Sudoku puzzle and provides solution.}
      \item {Uses OpenCV computer vision library and image processing to identify puzzle and Tesseract OCR to identify numbers.}
      \item {Customized image processing algorithms—used a combination of OpenCV functions and custom algorithms.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{http://github.com/ernestwong/connectd}{http://github.com/ernestwong/connectd}} % Organization/group
    { Social Media Platform Web Application | Connectd } % Affiliation/role
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Ruby on Rails mobile web application that allows user to search for other users and send invitations on all major social media platforms with a single button.}
      \item {Used oAuth authorization system for user authentication.}
      \item {Used social media API services (Facebook, Twitter, G+, LinkedIn) to send invitations to users.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{http://github.com/ernestwong/musedreams}{http://github.com/ernestwong/musedreams}} % Organization/group
    { An IoT hack with Muse headband | MuseDreams } % Affiliation/role
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item {Hardware hack using Muse headband that detects when user is about to fall asleep and makes adjustments to external surroundings. }
      \item {Analyzed EEG data and developed algorithm that recognizes user's sleepiness using state machine. }
      \item {Python server which interprets EEG data and posts state to Rails API for Android application. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{http://github.com/ernestwong/projecteuler}{http://github.com/ernestwong/projecteuler}} % Affiliation/role
    {Project Euler | A collection of logic/coding puzzles } % Organization/group
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Solutions to 40-50 math problems found on \href{http://projecteuler.net}{http://projecteuler.net}. Solutions written in C, C++, C\#, and Java}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
